---
title: "Text Mining for R"
author: "Iheb Jridi"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,warning = FALSE)
```


## Text Mining - Apple Product



**Problem**

Apple is considered today as the largest manufacturer of electronic products and software . 

In fact, the company's market capitalization exceeded trillion dollars in August 2018.


The apple company builds high-performance luxury computer equipment: the iPhone for example, sells at 590 units per minute.


It will be interesting to find out what people think of this company, by finding the most appropriate words  associated with the term **Apple**. The problem therefore comes down to finding the theme of the flow of comments from Internet users (Twitter in our case).

Given the size of content to be studied, the task turns out to be difficult. 

The use of text mining is therefore
paramount. 

# Presentation of the proposed solution 
Multiple text mining methods exist and allow to identify the theme of a textual data flow. In this lab, we will focus on the cloud
keywords (better known as **WordCloud**).

The keyword cloud is a visual representation of the keywords most used in a data flow.

Generally, words are displayed in font sizes and weights that are more visible when they are so used or popular (so depending on their frequency of appearance).

**Technical Details**

In this part, we will carefully explain the procedure to do. The operation consists of 3 main stages

**Imports**
```{r}
library("NLP")
library ("tm")
library("wordcloud")
library ("RColorBrewer")
```


**Loading data**
```{r}
data <-  readLines("apple.txt")
```



**Corpus Creation**

A corpus is a large and structured set of textual data. The purpose of this step is to convert semi-structured data into structured data that is easy to clean and handle.
```{r}
docs <- Corpus ( VectorSource (data))
```




**Cleaning and Transforming**

The transformation and cleaning stage consists of:
* The removal of stopwords
* The removal of punctuations
* The deletion of figures
* The deletion of spaces
* Removal of special characters
* The universalization of the case (in miniscule)


In our case, we will also delete the word apple, for more meaningful results.

```{r}
toSpace <- content_transformer ( function (x , pattern ) gsub (pattern, "", x))
docs <- tm_map (docs, content_transformer (tolower))
```
Text Processing

```{r}
# Supprimer les stopwords
docs <- tm_map (docs,removeWords, stopwords ("english"))

# Supprimer les ponctuations
docs <- tm_map (docs, removePunctuation)

# Supprimer les chiffres
docs <- tm_map (docs, removeNumbers)

# Réduire les espaces
docs <- tm_map (docs, stripWhitespace)


```

Reduce these following characters to one space.
```{r}
docs <- tm_map (docs, toSpace, "\n")


docs <- tm_map (docs, toSpace, "\t")

docs <- tm_map (docs, toSpace, "@")

docs <- tm_map (docs, toSpace, "apple")


docs <- tm_map (docs, toSpace, "#")


docs <- tm_map(docs, toSpace, "http")
```


**Construction of the word matrix**

This matrix contains the frequencies of the words in the corpus. The individuals are the documents; the columns
represent the words.

The _TermDocumentMatrix_ function takes the corpus as a parameter and allows you to create the matrix.

Then, we sort the matrix in decreasing order of frequencies and we create a dataframe from of the sorted matrix. This dataframe will ultimately allow you to create the wordcloud.
```{r}
dtm <- TermDocumentMatrix (docs)
m <- as.matrix(dtm)
v <- sort( rowSums (m),decreasing=TRUE)
d <- data.frame(word = names (v),freq=v)
```




**20 most frequent words**
 

```{r}
findFreqTerms(dtm, lowfreq = 20)
```

```{r}
barplot(d[1:10,]$freq, las = 2, names.arg = d[1:10,]$word,
col ="lightblue", main ="Most frequent words",
ylab = "Word frequencies")
```



**Results**

**Words associated with Apple**
```{r}
dtm
findAssocs (dtm, terms = c("apple","phone","new"), corlimit = c(0.1,0.3,0.2))

```



**WordCloud**
```{r}
set.seed (1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 10,
max.words=200, random.order=FALSE, rot.per=0.35,
colors= brewer.pal(8, "Dark2"))
```

**Interpretations**

By observing the wordcloud and the table of words associated with the term **Apple**, we can see that the flow
text on which we are studying, was downloaded during a promotion concerning the iPod, the gadget Apple music.

On the other hand, this same period saw the launch of the iTunes Festival event and the iTunes Music application (also known as Apple Music) which explains the high correlation
of the term **itunes**.

It is also important to mention that the term **iPhone** has the highest frequency.

This explains the success of this smartphone which is _always_ the news.



